Timeliness of security updates for Android

### 2014-11-14 securityupdates.tex
Add note to reviewers for avo and change the avo macro

\input{dastats}
\newcommand{\da}{Device Analyzer}
\newcommand{\dafoot}{\textsuperscript{\ref{foot:dadata}}}
\input{avostats}
\newcommand{\avo}{\texttt{androidvulnerabilities.org}}
\newcommand{\percMarketShare}{83.6\%~\footnote{\url{http://www.theinquirer.net/inquirer/news/2379036/android-hits-836-percent-marketshare-while-ios-windows-and-blackberry-slide}}}
\newcommand{\daNumDevices}{\daNumOSDevices}
\newcommand{\daDeviceDays}{\daOSTotalDaysData}
% Num versions since \daStartDate
\input{countversions}
\newcommand{\otherProjNum}{\avoNumExternalProjects}%TODO check we are doing the right calculation here and not overcounting

@@

We developed and maintain an open platform for filing critical vulnerabilities in a machine readable format, \texttt{\url{http://androidvulnerabilities.org/}}.
We seeded it with data from the CVE database, vendor lists, reports from the literature and various forums.
We have received submissions or amendments from \avoNumSubmitters\ individuals.
We collected this data between \avoStartDate\ and \avoEndDate\ and so any information lost before the start of that period cannot be included.
\avo\ currently contains \avoNumVulnerabilities\ vulnerabilities of which \avoNumVulnAllAndroid\ affect all Android devices and \avoNumVulnSpecific\ are specific to particular devices or device manufacturers.
We only use the \daNumVulnsUsed\ vulnerabilities which we have sufficient data to use for this analysis because they affect all Android devices rather than particular device manufacturers and we know enough information about the vulnerability to tie it to the particular versions it affects.
We summarise the \daNumVulnsUsed\ vulnerabilities used for this analysis in Table~\ref{tab:andvulns}.\todolater{We have published full details of the \daNumVulnsUsed\ vulnerabilities used for this analysis in an accompanying technical report~\cite{TODO}}

>>>>

\input{dastats}
\newcommand{\da}{Device Analyzer}
\newcommand{\dafoot}{\textsuperscript{\ref{foot:dadata}}}
\input{avostats}
\newcommand{\avo}{AVO}
\newcommand{\percMarketShare}{83.6\%~\footnote{\url{http://www.theinquirer.net/inquirer/news/2379036/android-hits-836-percent-marketshare-while-ios-windows-and-blackberry-slide}}}
\newcommand{\daNumDevices}{\daNumOSDevices}
\newcommand{\daDeviceDays}{\daOSTotalDaysData}
% Num versions since \daStartDate
\input{countversions}
\newcommand{\otherProjNum}{\avoNumExternalProjects}%TODO check we are doing the right calculation here and not overcounting

@@

We developed and maintain an open platform for filing critical vulnerabilities in a machine readable format, the AndroidVulnerabilities.org\footnote{\url{http://androidvulnerabilities.org/} \textbf{Note to reviewers: do not visit the contact page of this website}} (\avo) website.
We seeded it with data from the CVE database, vendor lists, reports from the literature and various forums.
We have received submissions or amendments from \avoNumSubmitters\ individuals.
We collected this data between \avoStartDate\ and \avoEndDate\ and so any information lost before the start of that period cannot be included.
\avo\ currently contains \avoNumVulnerabilities\ vulnerabilities of which \avoNumVulnAllAndroid\ affect all Android devices and \avoNumVulnSpecific\ are specific to particular devices or device manufacturers.
We only use the \daNumVulnsUsed\ vulnerabilities which we have sufficient data to use for this analysis because they affect all Android devices rather than particular device manufacturers and we know enough information about the vulnerability to tie it to the particular versions it affects.
We summarise the \daNumVulnsUsed\ vulnerabilities used for this analysis in Table~\ref{tab:andvulns}.\todolater{We have published full details of the \daNumVulnsUsed\ vulnerabilities used for this analysis in an accompanying technical report~\cite{TODO}}
